Characteristic polynomials of p-adic matrices

### 2017-02-01 charpoly/charpoly.tex
Minor

The second ingredient we need is the reciprocal polynomial.
We extend its definition to matrices of polynomials.
\begin{deftn}
$n$ being fixed, let $P \in K[X]$ be of degree $d \leq n.$ 
We define its reciprocal polynomial as $P^{rec}=X^n P \left( 1/X \right).$
Let $A \in M_n(K[X]).$ We denote by $A^{rec}$ the matrix
whose coefficients are the reciprocal polynomials of the
coefficients of $A.$ 
\end{deftn}
We then have the following result :
\begin{lem}
Let $M \in M_n(K).$ Then:
\begin{eqnarray*}
com(1-XM)^{rec}=&com(X-M), \\
(\chi_M \times 1)^{rec}=&(1-XM) com(1-XM).\\
\end{eqnarray*}
\end{lem}

>>>>

The second ingredient we need is the reciprocal polynomial.
We extend its definition to matrices of polynomials.
\begin{deftn}
Let $P \in K[X]$ be of degree $d \leq n.$ 
We define its reciprocal polynomial as $P^{rec}=X^d P \left( 1/X \right).$
Let $A \in M_n(K[X]).$ We denote by $A^{rec}$ the matrix
whose coefficients are the reciprocal polynomials of the
coefficients of $A.$ 
\end{deftn}
We then have the following result :
\begin{lem}
Let $M \in M_n(K).$ Then:
\begin{eqnarray*}
com(1-XM)^{rec}=&com(X-M), \\
(\chi_M \times 1)^{rec}=&(1-XM) com(1-XM).\\
\end{eqnarray*}
\end{lem}
